Deep Reinforcement Learning for Conservation Decisions

### 2021-01-25 manuscript/manuscript.Rmd
Small edits

In practice, the general process for attaining a good performing agent is to tune model hyperparameters then train an agent using the best hyperparameters. Hyperparameters refer to the parameters in a RL algorithm that are not directly learned during the training process. For example, a weight in the neural network is a model parameter, but the number of hidden layers in the neural network is a hyperparameter. Since the optimal hyperparameters cannot be found analytically, tuning should be done to find a good-performing set of hyperparameters. The hyperparameter tuning process consists of sampling then evaluating a set of hyperparameters, where tuning trials are often ranked by mean cumulative reward. It is important to note that hyperparameter tuning can often be a very time intensive process. Since one round of training can be time intensive, hyperparameter tuning, which consists of usually numerous rounds of training, can be very time intensive.

>>>>

In practice, the general process for attaining a good performing agent is to tune model hyperparameters then train an agent using the best hyperparameters. Hyperparameters refer to the parameters in a RL algorithm that are not directly learned during the training process. For example, a weight in the neural network is a model parameter, but the number of hidden layers in the neural network is a hyperparameter. Since the optimal hyperparameters cannot be found analytically, tuning should be done to find a good-performing set of hyperparameters. The hyperparameter tuning process consists of sampling then evaluating a set of hyperparameters, where tuning trials are often ranked by mean cumulative reward. Since one round of training can be time intensive, hyperparameter tuning, which consists of usually numerous rounds of training, can be particularly time intensive.
